---
title: "Linear Model"
author: "Jocelyn Lazcano"
date: "3/25/2021"
output:
    html_document:
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.


```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```


# model1

### Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

### Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
Scatter plot shows a positive relationship between ARM and SIM. Equation of the line is SIMS= -4.1+0.05*ARM. The adjusted R Square is 0.467, the standard error is 1.226. The residual standard error is the standard deviation of normal spread of errors on the line. 
  
### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

### Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


```{r}
newdata=data.frame(GRIP=94,ARM=88)
predict(model.1,newdata,interval="prediction")
```



### now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

The scatter plots shows a positive realtionship between SIMS and ARM. The equation 

The equation for SIMS is explained by ARM is SIMS = -4.1+.0545*ARM.

# model2

### Now with ggplot - first select the basic data

```{r}
basicGG <- ggplot(data,aes(y=SIMS,x=GRIP))
```

### Now add in scatterplot

```{r}
basicGG + geom_point()
```

### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

### Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2,newdata,interval="prediction")
```


### now add the model fit to our plot
  
```{r}
basicGG + geom_point() + geom_smooth(method=lm)
``` 

The equation for SIMS is explained by GRIP is SIMS = -4.18+.0545*GRIP.

# model 3

### Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3,newdata,interavl="prediction")
```

SIMS=-5.43+0.037 * ARM+0.024 * GRIP

# Compare the models

```{r}
anova(model.1,model.3)
predict(model.3,newdata,interavl="prediction")
```

The anova compares model 1 with model 3, the null hypothesis has no difference in the ability to predict SIMS. The alternative hypothesis is that there is a difference. The p-value is 0.000005 this is so small that the difference in the ability to predict SIMS is not due to chance. The adjusted r squared and standard deviation of the errors both indicate that the ARM+GRIP model is better. The prediction for ARM+GRIP model is 0.15 and the 95% confidence interval is -2.1 to 2.4. 

